---
title: "00_Demo_data"
author: "Kendra Seaman"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

# Temporal Discounting Social Distancing Study `r sample`

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('../03_graph_demo.R')
```

## Age distribution

```{r graph age, echo = FALSE}
ageplot
```

The sample ranged in age from `r agerange[1]` to `r agerange[2]` with a mean age of **`r round(meanage, 2)`**. 

## Sex distribution

```{r graph sex, echo = FALSE}
sexplot
```

The sample had **`r sex_freq[1,2]` women (`r round(sex_freq[1,2] / (sex_freq[1,2] + sex_freq[2,2]) * 100, 2)`%)**.  

## Education distribution

```{r graph ed, echo = FALSE}
edplot
```

The vast majority participants had some college **(`r sum(ed_freq$percent[3:6])*100`%)**.

## Race distribution

```{r graph race, echo = FALSE}
raceplot
```

The samples were almost equally distributed between **White (`r race_freq[3,4]*100`%), Black (`r race_freq[2,4]*100`%), or Hispanic/Latino (`r race_freq[3,4]*100`%)**.

## Income distribution

```{r graph income, echo = FALSE}
incomeplot
```

The most frequent income band selected was **`r modeincome[1]`**.  

The median income band was **`r dollar((medianincome-5) * 1000)` - `r dollar((medianincome+5) * 1000)`**

## Employment distribution

```{r graph employ, echo = FALSE}
employplot
```

The most frequent employment was **`r modeemploy[1]`**.  

**`r round(fulltime * 100, 2)`%** were employeed full time.  

**`r round(retired * 100, 2)`%** were retired.

## Class distribution
```{r graph class, echo = FALSE}
classplot
```

The most frequent class was **`r modeclass[1]`**, **`r round((class_freq[4,2] / sum(class_freq$freq))*100, 2)`%**.