---
title: "TempDisc"
author: "Kendra Seaman"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

# Temporal Discounting Social Distancing Study `r sample`

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
```

```{r scripts, include = FALSE}
source("../04_graph_temp_disc.R")
source("../05_td_ancova.R")
source("../06_td_age_by_domain.R")
```

# Domain (Money x Health x Social) ANCOVA with Age 
```{r mean graph, echo = FALSE, warnings = FALSE}
td_means
```

```{r ancova, echo = FALSE}
m1$ANOVA %>%
  kable() %>%
  kable_styling() %>%
  row_spec(1:3, bold = T, background = "yellow")
```

### Sphericity check
```{r spher, echo = FALSE}
m1$`Mauchly's Test for Sphericity`%>%
  kable() %>%
  kable_styling() %>%
  row_spec(1:2, bold = T, background = "yellow")
```

### Sphericity correction
```{r spher correction, echo = FALSE}
m1$`Sphericity Corrections` %>%
  kable() %>%
  kable_styling() %>%
  row_spec(1:2, bold = T, background = "yellow")
```

### Follow-up Test
```{r followup, echo = FALSE}
if (sample == 1) {
  fu %>%
    kable() %>%
    kable_styling() %>%
    row_spec(1:2, bold = T, background = "yellow") 
} else {
    fu %>%
    kable() %>%
    kable_styling() %>%
    row_spec(1:3, bold = T, background = "yellow") 
}
```

***
***

# Age effects
```{r agegraph, echo = FALSE, warnings = FALSE}
td_x_age
```

### Money

Model - Age
```{r money1, echo = FALSE}
summary(money_models[[1]])$coefficients %>%
  kable() %>%
  kable_styling()
```

Model - Age + Age^2
```{r money2, echo = FALSE}
summary(money_models[[3]])$coefficients %>%
  kable() %>%
  kable_styling()
```

No efffect of age on money discounting.

```{r money3, echo = FALSE, warnings = FALSE}
moneyuseplot
```

Q2169_1 = `r dd$Question[grep('Q169_1', dd$Variable)]` 

Mean importance of social contact is `r moneymean` on a scale from 0 (Not important) to 100 (Extremely important)

```{r money4, echo = FALSE}
moneyimportplot
```

Correlation between age and importance of money, r(`r moneycor$n[1,2]`) = `r moneycor$r[1,2]`, p = `r moneycor$P[1,2]`.

### Health 

Model - Age
```{r health1, echo = FALSE}
summary(health_models[[1]])$coefficients %>%
  kable() %>%
  kable_styling() %>%
  row_spec(2, bold = T, background = "yellow")
```

Model - Age + Age^2
```{r health2, echo = FALSE}
summary(health_models[[3]])$coefficients %>%
  kable() %>%
  kable_styling() %>%
  row_spec(2, bold = T, background = "yellow")
```

Model comparison
```{r health3, echo = FALSE}
anova(health_models[[1]], health_models[[3]]) %>% 
  kable() %>%
  kable_styling
```

Significant linear effect of age on health discounting, with older adults discounting more than younger adults.

Q2169_2 = `r dd$Question[grep('Q169_2', dd$Variable)]` 

Mean importance of social contact is `r healthmean` on a scale from 0 (Not important) to 100 (Extremely important)

```{r health4, echo = FALSE, warning = FALSE}
healthimportplot
```

Correlation between age and importance of health, r(`r healthcor$n[1,2]`) = `r healthcor$r[1,2]`, p = `r healthcor$P[1,2]`.

### Social

Model - Age
```{r social1, echo = FALSE}
summary(social_models[[1]])$coefficients %>%
  kable() %>%
  kable_styling() %>%
  row_spec(2, bold = T, background = "yellow")
```

Model - Age + Age^2
```{r social2, echo = FALSE}
if (sample == 1) {
  summary(social_models[[3]])$coefficients %>%
    kable() %>%
    kable_styling() %>%
    row_spec(2:3, bold = T, background = "yellow")
} else {
  summary(social_models[[3]])$coefficients %>%
    kable() %>%
    kable_styling() %>%
    row_spec(2, bold = T, background = "yellow")
}
```

Model comparison
```{r social3, echo = FALSE}
anova(social_models[[1]], social_models[[3]]) %>% 
  kable() %>%
  kable_styling %>%
  row_spec(2, bold = T, background = "yellow")
```

Significant linear and quadratic effects of age on social discounting, with older adults discounting more than younger adults and middle aged adults discounting more than younger or older adults

# Who are the social partners?
```{r social4, echo = FALSE}
partplot
```

Q2169_3 = `r dd$Question[grep('Q169_3', dd$Variable)]` 

Mean importance of social contact is `r socialmean` on a scale from 0 (Not important) to 100 (Extremely important)

```{r social5, echo = FALSE, warnings = FALSE}
socialimportplot
```

Correlation between age and importance of social contact, r(`r socialcor$n[1,2]`) = `r socialcor$r[1,2]`, p = `r socialcor$P[1,2]`.