---
title: "Social Distance and Age"
author: "Kendra Seaman"
date:  "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

# Temporal Discounting Social Distancing Study `r sample`

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
```

```{r scripts, include = FALSE}
source("../08_social_dist_correlations.R")
source("../scr/multiplot.R")

fancy_graph <- function(plot1, plot2, ylabel, color_var) {
  g1 <- plot1 + geom_jitter(aes(color = color_var)) + geom_smooth(method=lm, color = "black") +
    theme_minimal() + theme(legend.position = 'none') +
    ylab(ylabel) + xlab("Age")
  g2 <- plot2 + geom_histogram(stat='count') + coord_flip() + 
    theme_minimal() + theme(legend.position = 'none', axis.title.y = element_blank(), 
                            axis.text.y = element_blank()) + xlab('Count') 
  multiplot(g1,g2, cols = 2)
}
```

```{r correlations, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table1[c(1:10, 14:16), 1:2] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(8, 10, 12), bold = T, background = "yellow")
} else {
  table1[c(1:10, 14:16), 1:2] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(8, 10, 12), bold = T, background = "yellow")
}
```

Q23_1 = `r dd$Question[grep('Q23_1', dd$Variable)]`

```{r likely covid, echo = FALSE, warnings = FALSE, message = FALSE}
names = c('cc1.RDS', 'cc2.RDS')
if (sample == 1) {names = paste0('../output/s1_', names) }else { names = paste0('../output/s2_', names) }
color <- factor(dt$Q23_1)
p1 <- readRDS(names[1])
p2 <- readRDS(names[2])
fancy_graph(p1, p2, dd$variable_name[grep('Q23_1', dd$Variable)], color)
```

Q25 = `r dd$Question[grep('Q25', dd$Variable)]`

`r dd$allowed_values[grep('Q25', dd$Variable)]`

```{r covid outcome, echo = FALSE, warning = FALSE, , message = FALSE}
names = c('co1.RDS', 'co2.RDS')
if (sample == 1) {names = paste0('../output/s1_', names) }else { names = paste0('../output/s2_', names) }
color <- factor(dt$Q25)
p1 <- readRDS(names[1])
p2 <- readRDS(names[2])
fancy_graph(p1, p2, dd$variable_name[grep('Q25', dd$Variable)], color)
```

SC1 = `r dd$Question[grep('Q26', dd$Variable)]` 

```{r mental health, echo = FALSE, warning = FALSE, message = FALSE}
names = c('mh1.RDS', 'mh2.RDS')
if (sample == 1) {names = paste0('../output/s1_', names) }else { names = paste0('../output/s2_', names) }
color <- factor(dt$SC1)
p1 <- readRDS(names[1])
p2 <- readRDS(names[2])
fancy_graph(p1, p2, dd$variable_name[grep('SC1', dd$Variable)], color)
```

```{r correlations2, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table2[c(1:7, 14:15), 1:2] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(2, 3, 6), bold = T, background = "yellow")
} else {
  table2[c(1:7, 14:15), 1:2] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(2, 3, 6), bold = T, background = "yellow")
}
```

Q16_1 = `r dd$Question[grep('Q16_1', dd$Variable)]` 
lower scores = higher rank

```{r work, echo = FALSE, warning = FALSE, message = FALSE}
names = c('work1.RDS', 'work2.RDS')
if (sample == 1) {names = paste0('../output/s1_', names) }else { names = paste0('../output/s2_', names) }
color <- factor(dt$Q16_1)
p1 <- readRDS(names[1])
p2 <- readRDS(names[2])
fancy_graph(p1, p2, dd$variable_name[grep('Q16_1', dd$Variable)], color)
```

Q16_2 = `r dd$Question[grep('Q16_2', dd$Variable)]` 
lower scores = higher rank  
**Q16_2's correlation with age is not significant in replication sample.**

Q16_5 = `r dd$Question[grep('Q16_5', dd$Variable)]` 
lower scores = higher rank

```{r community, echo = FALSE, warning = FALSE, message = FALSE}
names = c('com1.RDS', 'com2.RDS')
if (sample == 1) {names = paste0('../output/s1_', names) }else { names = paste0('../output/s2_', names) }
color <- factor(dt$Q16_2)
color <- factor(dt$Q16_5)
p1 <- readRDS(names[1])
p2 <- readRDS(names[2])
fancy_graph(p1, p2, dd$variable_name[grep('Q16_5', dd$Variable)], color)
```

```{r correlations3, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table3[c(1:7), 1:2] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(2,3, 7), bold = T, background = "yellow")
} else {
  table3[c(1:7), 1:2] %>%
    kable() %>%
    kable_styling()
}
```


Q20_1 = `r dd$Question[grep('Q20_1', dd$Variable)]` 
(lower scores = higher rank)  
**Q20_1 is not significant in replication sample.**  

Q20_2 = `r dd$Question[grep('Q20_2', dd$Variable)]`  
**Q20_2 is not significant in replication sample**  

Q20_6 = `r dd$Question[grep('Q20_6', dd$Variable)]` 
(lower scores = higher rank)  
**Q20_6 is not significant in replication sample**  

```{r correlations4, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table4[c(1:6), 1:2] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(2,3), bold = T, background = "yellow")
} else {
  table4[c(1:6), 1:2] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(2,3), bold = T, background = "yellow")
}
```

Q22_1 = `r dd$Question[grep('Q22_1', dd$Variable)]` 
(lower scores = higher rank)

```{r self, echo = FALSE, warning = FALSE, message = FALSE}
names = c('sh1.RDS', 'sh2.RDS')
if (sample == 1) {names = paste0('../output/s1_', names) }else { names = paste0('../output/s2_', names) }
color <- factor(dt$Q22_1)
p1 <- readRDS(names[1])
p2 <- readRDS(names[2])
fancy_graph(p1, p2, dd$variable_name[grep('Q22_1', dd$Variable)], color)
```


Q22_2 = `r dd$Question[grep('Q22_2', dd$Variable)]` 
(lower scores = higher rank)

```{r famliy, echo = FALSE, warning = FALSE, message = FALSE}
names = c('fh1.RDS', 'fh2.RDS')
if (sample == 1) {names = paste0('../output/s1_', names) }else { names = paste0('../output/s2_', names) }
color <- factor(dt$Q22_2)
p1 <- readRDS(names[1])
p2 <- readRDS(names[2])
fancy_graph(p1, p2, dd$variable_name[grep('Q22_2', dd$Variable)], color)
```