---
title: "Social Distance and Age"
author: "Kendra Seaman"
date: "5/26/2020"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
```

```{r scripts, include = FALSE}
source("../07_social_dist_correlations.R")
source("../scr/multiplot.R")

fancy_graph <- function(plot1, plot2, ylabel, color_var) {
  g1 <- plot1 + geom_jitter(aes(color = color_var)) + geom_smooth(method=lm, color = "black") +
    theme_minimal() + theme(legend.position = 'none') +
    ylab(ylabel) + xlab("Age")
  g2 <- plot2 + geom_histogram(stat='count') + coord_flip() + 
    theme_minimal() + theme(legend.position = 'none', axis.title.y = element_blank(), 
                            axis.text.y = element_blank()) + xlab('Count') 
  multiplot(g1,g2, cols = 2)
}
```

```{r correlations, echo = FALSE, warnings = FALSE}
table1[1:13, 1:2] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(8, 10, 12), bold = T, background = "yellow")
```

Q23_1 = `r dd$Question[grep('Q23_1', dd$Variable)]`

```{r likely covid, echo = FALSE, warnings = FALSE}
color <- factor(dt$Q23_1)
p1 <- readRDS("../output/cc1.RDS")
p2 <- readRDS("../output/cc2.RDS")
fancy_graph(p1, p2, dd$variable_name[grep('Q23_1', dd$Variable)], color)
```

Q25 = `r dd$Question[grep('Q25', dd$Variable)]`

`r dd$allowed_values[grep('Q25', dd$Variable)]`

```{r covid outcome, echo = FALSE, warning = FALSE}
color <- factor(dt$Q25)
p1 <- readRDS("../output/co1.RDS")
p2 <- readRDS("../output/co2.RDS")
fancy_graph(p1, p2, dd$variable_name[grep('Q25', dd$Variable)], color)
```

SC1 = `r dd$Question[grep('Q26', dd$Variable)]` 

```{r mental health, echo = FALSE, warning = FALSE}
color <- factor(dt$SC1)
p1 <- readRDS("../output/mh1.RDS")
p2 <- readRDS("../output/mh2.RDS")
fancy_graph(p1, p2, dd$variable_name[grep('SC1', dd$Variable)], color)
```

```{r correlations2, echo = FALSE, warnings = FALSE}
table2[1:2] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(2,3,6), bold = T, background = "yellow")
```

Q16_1 = `r dd$Question[grep('Q16_1', dd$Variable)]` 
lower scores = higher rank

```{r work, echo = FALSE, warning = FALSE}
color <- factor(dt$Q16_1)
p1 <- readRDS("../output/work1.RDS")
p2 <- readRDS("../output/work2.RDS")
fancy_graph(p1, p2, dd$variable_name[grep('Q16_1', dd$Variable)], color)
```

Q16_2 = `r dd$Question[grep('Q16_2', dd$Variable)]` 
lower scores = higher rank

```{r essential, echo = FALSE, warning = FALSE}
color <- factor(dt$Q16_2)
p1 <- readRDS("../output/ei1.RDS")
p2 <- readRDS("../output/ei2.RDS")
fancy_graph(p1, p2, dd$variable_name[grep('Q16_2', dd$Variable)], color)
```

Q16_5 = `r dd$Question[grep('Q16_5', dd$Variable)]` 
lower scores = higher rank

```{r community, echo = FALSE, warning = FALSE}
color <- factor(dt$Q16_5)
p1 <- readRDS("../output/com1.RDS")
p2 <- readRDS("../output/com2.RDS")
fancy_graph(p1, p2, dd$variable_name[grep('Q16_5', dd$Variable)], color)
```

```{r correlations3, echo = FALSE, warnings = FALSE}
table3[1:2] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(2,7), bold = T, background = "yellow")
```


Q20_1 = `r dd$Question[grep('Q20_1', dd$Variable)]` 
(lower scores = higher rank)

```{r work2, echo = FALSE, warning = FALSE}
color <- factor(dt$Q20_1)
p1 <- readRDS("../output/vw1.RDS")
p2 <- readRDS("../output/vw2.RDS")
fancy_graph(p1, p2, dd$variable_name[grep('Q20_1', dd$Variable)], color)
```

Q20_6 = `r dd$Question[grep('Q20_6', dd$Variable)]` 
(lower scores = higher rank)

```{r care, echo = FALSE, warning = FALSE}
color <- factor(dt$Q20_6)
p1 <- readRDS("../output/ec1.RDS")
p2 <- readRDS("../output/ec2.RDS")
fancy_graph(p1, p2, dd$variable_name[grep('Q20_6', dd$Variable)], color)
```

```{r correlations4, echo = FALSE, warnings = FALSE}
table4[1:2] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(2,3), bold = T, background = "yellow")
```

Q22_1 = `r dd$Question[grep('Q22_1', dd$Variable)]` 
(lower scores = higher rank)

```{r self, echo = FALSE, warning = FALSE}
color <- factor(dt$Q22_1)
p1 <- readRDS("../output/sh1.RDS")
p2 <- readRDS("../output/sh2.RDS")
fancy_graph(p1, p2, dd$variable_name[grep('Q22_1', dd$Variable)], color)
```


Q22_2 = `r dd$Question[grep('Q22_2', dd$Variable)]` 
(lower scores = higher rank)

```{r famliy, echo = FALSE, warning = FALSE}
color <- factor(dt$Q22_2)
p1 <- readRDS("../output/fh1.RDS")
p2 <- readRDS("../output/fh2.RDS")
fancy_graph(p1, p2, dd$variable_name[grep('Q22_2', dd$Variable)], color)
```