---
title: "Temporal Discounting and Social Distancing"
author: "Kendra Seaman"
date: "5/28/2020"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
```

```{r scripts, include = FALSE}
source("../07_social_dist_correlations.R")
```

# Monetary discounting (SC3)
```{r money, echo = FALSE, warnings = FALSE}
table1[c(2:14), c(1,15)] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(7), bold = T, background = "yellow")
```

Q23_1 = `r dd$Question[grep('Q23_1', dd$Variable)]`  
Q23_1 = `r dd$allowed_values[grep('Q23_1', dd$Variable)]`

**People with higher monetary discount rates are less likely to think they will catch COVID-19.**

```{r money2, echo = FALSE, warnings = FALSE}
table2[c(2:7), c(1,9)] %>%
  kable() %>%
  kable_styling() 
```

```{r money3, echo = FALSE, warnings = FALSE}
table3[c(2:7), c(1,9)] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(2,3,5,6), bold = T, background = "yellow")
```

(lower scores = higher rank)  
Q20_2 = `r dd$Question[grep('Q20_2', dd$Variable)]`  

**People with higher monetary discount rates are more likely to rank having people visit to deliver essential items higher.**

Q20_3 = `r dd$Question[grep('Q20_3', dd$Variable)]`  

**People with higher monetary discount rates are less likely to rank having people visit for social contact higher.**

Q20_5 = `r dd$Question[grep('Q20_5', dd$Variable)]`  

**People with higher monetary discount rates are more likely to rank having people visit for community service higher.**

Q20_6 = `r dd$Question[grep('Q20_6', dd$Variable)]`  

**People with higher monetary discount rates are more likely to rank having people visit for essential care higher.**

# Health discounting (SC4)
```{r healht1, echo = FALSE, warnings = FALSE}
table1[c(2:14), c(1,16)] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(1:2), bold = T, background = "yellow")
```

Q10 = `r dd$Question[grep('Q10', dd$Variable)][1]`  
Q10 = `r dd$allowed_values[grep('Q10', dd$Variable)][1]`  

**People with higher health discounting rates are less likely to have COVID-19.**

Q11 = `r dd$Question[grep('Q11', dd$Variable)][1]`  
Q11 = `r dd$allowed_values[grep('Q11', dd$Variable)][1]`  

**People with higher health discounting rates are less likely to have contracted COVID-19.**

```{r health2, echo = FALSE, warnings = FALSE}
table2[c(2:7), c(1,10)] %>%
  kable() %>%
  kable_styling() 
```

```{r health3, echo = FALSE, warnings = FALSE}
table3[c(2:7), c(1,10)] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(1,3,5,6), bold = T, background = "yellow")
```

(lower scores = higher rank)  

Q20_1 = `r dd$Question[grep('Q20_1', dd$Variable)]`  

**People with higher health discount rates are less likely to highly rank having people visit for work.**

Q20_3 = `r dd$Question[grep('Q20_3', dd$Variable)]`  

**People with higher health discount rates are less likely to highly rank having people visit for social contact.**

Q20_5 = `r dd$Question[grep('Q20_5', dd$Variable)]`  

**People with higher health discount rates are more likely to highly rank having people visit for community service.**

Q20_6 = `r dd$Question[grep('Q20_6', dd$Variable)]`  

**People with higher health discount rates are more likely to highly rank having people visit for essential care.**

# Social discounting (SC5)
```{r social1, echo = FALSE, warnings = FALSE}
table1[c(2:14), c(1,17)] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(1), bold = T, background = "yellow")
```

Q10 = `r dd$Question[grep('Q10', dd$Variable)][1]`
Q10 = `r dd$allowed_values[grep('Q10', dd$Variable)][1]`  

**People with higher social discounting rates are less likely to have COVID-19.**

```{r social2, echo = FALSE, warnings = FALSE}
table2[c(2:7), c(1,11)] %>%
  kable() %>%
  kable_styling() 
```

```{r social3, echo = FALSE, warnings = FALSE}
table3[c(2:7), c(1,11)] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(1,6), bold = T, background = "yellow")
```

Q20_1 = `r dd$Question[grep('Q20_1', dd$Variable)]`  

**People with higher social discount rates are less likely to highly rank having people visit for work.**

Q20_6 = `r dd$Question[grep('Q20_6', dd$Variable)]`  

**People with higher social discount rates are more likely to highly rank having people visit for essential care.**

# Discounting difference (Social Discounting - Health Discounting; discountdiff)
```{r diff, echo = FALSE, warnings = FALSE}
table1[c(2:14), c(1,18)] %>%
  kable() %>%
  kable_styling() 
```

```{r diff2, echo = FALSE, warnings = FALSE}
table2[c(2:7), c(1,12)] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(5), bold = T, background = "yellow")
```

Q16_5 = `r dd$Question[grep('Q16_5', dd$Variable)]`  

**People with a larger difference between social and health discount rates are more likely to highly rank leaving for community service.**

```{r diff3, echo = FALSE, warnings = FALSE}
table3[c(2:7), c(1,12)] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(5), bold = T, background = "yellow")
```

Q20_5 = `r dd$Question[grep('Q20_5', dd$Variable)]`  

**People with a larger difference between social and health discount rates are less likely to highly rank having people visit for community service.**