---
title: "Temporal Discounting and Social Distancing"
author: "Kendra Seaman"
date:  "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---
# Temporal Discounting Social Distancing Study `r sample`

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
```

```{r scripts, include = FALSE}
source("../08_social_dist_correlations.R")
```

# Monetary discounting (SC3)
```{r money, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table1[c(2:16), c(1,18)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(7, 10), bold = T, background = "yellow")
} else {
  table1[c(2:16), c(1,18)] %>%
  kable() %>%
  kable_styling() 
}

```

Q23_1 = `r dd$Question[grep('Q23_1', dd$Variable)]`  
Q23_1 = `r dd$allowed_values[grep('Q23_1', dd$Variable)]`

People with higher monetary discount rates are less likely to think they will catch COVID-19. **Does not replicate.**  

Q169_1 = `r dd$Question[grep('Q169_1', dd$Variable)]`  

People with higher monetary discount rates view money as being more important.  **Does not replicate.**  

```{r money2, echo = FALSE, warnings = FALSE}
table2[c(2:7), c(1,12)] %>%
  kable() %>%
  kable_styling() 
```

```{r money3, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table3[c(2:7), c(1,12)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(2,3,5,6), bold = T, background = "yellow")
} else {
  table3[c(2:7), c(1,12)] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(5), bold = T, background = "yellow")
}

```

(lower scores = higher rank)  
Q20_2 = `r dd$Question[grep('Q20_2', dd$Variable)]`  

People with higher monetary discount rates are more likely to highly rank having people visit to deliver essential items.  **Does not replicate**  

Q20_3 = `r dd$Question[grep('Q20_3', dd$Variable)]`  

People with higher monetary discount rates are less likely to highly rank having people visit for social contact.  **Does not replicate.**  

Q20_5 = `r dd$Question[grep('Q20_5', dd$Variable)]`  

**People with higher monetary discount rates are more likely to highly rank having people visit for community service. Replicates. ** 

Q20_6 = `r dd$Question[grep('Q20_6', dd$Variable)]`  

People with higher monetary discount rates are more likely to highly rank having people visit for essential care.  **Does not replicate.**

```{r money4, echo = FALSE, warnings = FALSE}
table4[c(2:6), c(1,11)] %>%
  kable() %>%
  kable_styling() 
```

# Health discounting (SC4)
```{r healht1, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table1[c(2:16), c(1,19)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(1, 2), bold = T, background = "yellow")
} else { 
table1[c(2:16), c(1,19)] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(7, 9), bold = T, background = "yellow")
}
```

Q10 = `r dd$Question[grep('Q10', dd$Variable)][1]`  
Q10 = `r dd$allowed_values[grep('Q10', dd$Variable)][1]`  

People with higher health discounting rates are less likely to have COVID-19.  **Does not replicate**

Q11 = `r dd$Question[grep('Q11', dd$Variable)][1]`  
Q11 = `r dd$allowed_values[grep('Q11', dd$Variable)][1]`  

People with higher health discounting rates are less likely to have contracted COVID-19.  **Does not replicate.**

Q23_1 = `r dd$Question[grep('Q23_1', dd$Variable)][1]`  
Q23_1 = `r dd$allowed_values[grep('Q23_1', dd$Variable)][1]` 

**Relationship not found in primary sample.**  

Q25 = `r dd$Question[grep('Q25', dd$Variable)][1]`  
Q25 = `r dd$allowed_values[grep('Q25', dd$Variable)][1]` 

**Relationship not found in primary sample.**  

Q169_1 = `r dd$Question[grep('Q169_1', dd$Variable)][1]`  

People with higher health discounting rates are more likely to **Does not replicate.**

```{r health2, echo = FALSE, warnings = FALSE}
table2[c(2:7), c(1,13)] %>%
  kable() %>%
  kable_styling() 
```

```{r health3, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table3[c(2:7), c(1,13)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(1,3,5,6), bold = T, background = "yellow")
} else {
  table3[c(2:7), c(1,13)] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(3), bold = T, background = "yellow")
}
```

(lower scores = higher rank)  

Q20_1 = `r dd$Question[grep('Q20_1', dd$Variable)]`  

People with higher health discount rates are less likely to highly rank having people visit for work.  **Does not replicate.**  

Q20_3 = `r dd$Question[grep('Q20_3', dd$Variable)]`  

People with higher health discount rates are less likely to highly rank having people visit for social contact. **Replication sample showed the *opposite* relationship.**  

Q20_5 = `r dd$Question[grep('Q20_5', dd$Variable)]`  

People with higher health discount rates are more likely to highly rank having people visit for community service.  **Does not replicate.**  

Q20_6 = `r dd$Question[grep('Q20_6', dd$Variable)]`  

People with higher health discount rates are more likely to highly rank having people visit for essential care. **Does not replicate.**

```{r health4, echo = FALSE, warnings = FALSE}
table4[c(2:6), c(1,12)] %>%
  kable() %>%
  kable_styling() 
```

# Social discounting (SC5)
```{r social1, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table1[c(2:16), c(1,20)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(1), bold = T, background = "yellow")
} else {
  table1[c(2:16), c(1,20)] %>%
  kable() %>%
  kable_styling() 
}
```

Q10 = `r dd$Question[grep('Q10', dd$Variable)][1]`
Q10 = `r dd$allowed_values[grep('Q10', dd$Variable)][1]`  

People with higher social discounting rates are less likely to have COVID-19.  **Does not replicate**

```{r social2, echo = FALSE, warnings = FALSE}
table2[c(2:7), c(1,14)] %>%
  kable() %>%
  kable_styling() 
```

```{r social3, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table3[c(2:7), c(1,14)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(1,6), bold = T, background = "yellow")
} else {
    table3[c(2:7), c(1,14)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(3,6), bold = T, background = "yellow")
}
```

Q20_1 = `r dd$Question[grep('Q20_1', dd$Variable)]`  

People with higher social discount rates are less likely to highly rank having people visit for work.  **Does not replicate.**

Q20_3 = `r dd$Question[grep('Q20_3', dd$Variable)]` 

**Relationship not present in primary sample.**

Q20_6 = `r dd$Question[grep('Q20_6', dd$Variable)]`  

People with higher social discount rates are more likely to highly rank having people visit for essential care. **Opposite relationship found in replication sample.**

```{r social4, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table4[c(2:6), c(1,13)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(5), bold = T, background = "yellow")
} else {
  table4[c(2:6), c(1,13)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(1), bold = T, background = "yellow")
}
```

Q22_1 = `r dd$Question[grep('Q22_1', dd$Variable)]` 

**Relationship not found in primary sample.**

Q22_5 = `r dd$Question[grep('Q22_5', dd$Variable)]` 

People with higher social discount rates are less likely to highly rank staying home for other reasons.  **Does not replicate**

# Discounting difference (Social Discounting - Health Discounting; discountdiff)
```{r diff, echo = FALSE, warnings = FALSE}
table1[c(2:14), c(1,21)] %>%
  kable() %>%
  kable_styling() 
```

```{r diff2, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table2[c(2:7), c(1,15)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(5), bold = T, background = "yellow")
} else { 
  table2[c(2:7), c(1,15)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(5), bold = T, background = "yellow")
}
```

Q16_5 = `r dd$Question[grep('Q16_5', dd$Variable)]`  

People with a larger difference between social and health discount rates are more likely to highly rank leaving for community service. **Does not replicate.**

```{r diff3, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table3[c(2:7), c(1,15)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(5), bold = T, background = "yellow")
} else {
  table3[c(2:7), c(1,15)] %>%
    kable() %>%
    kable_styling() 
}
```

Q20_5 = `r dd$Question[grep('Q20_5', dd$Variable)]`  

People with a larger difference between social and health discount rates are less likely to highly rank having people visit for community service. **Does not replicates.**

```{r diff4, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table4[c(2:6), c(1,14)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(5), bold = T, background = "yellow")
} else { 
  table4[c(2:6), c(1,14)] %>%
    kable() %>%
    kable_styling() 
}
```

Q22_5 = `r dd$Question[grep('Q22_5', dd$Variable)]` 

People with a larger difference between social and health discount rates are less likely to highly rank staying home for other reasons. **Does not replicate.**
