---
title: "Values and Social Distancing"
author: "Kendra Seaman"
date:  "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

# Temporal Discounting Social Distancing Study `r sample`

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
```

```{r scripts, include = FALSE}
source("../08_social_dist_correlations.R")
```

## Importance of Money (Q169_1)
Q169_1 = `r dd$Question[grep('Q169_1', dd$Variable)][1]`  

```{r money, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table1[c(2:10,14:16), c(1,12)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(4, 11), bold = T, background = "yellow")
} else {
  table1[c(2:10,14:16), c(1,12)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(5, 8:11), bold = T, background = "yellow")
}
```

Q13 = `r dd$Question[grep('Q13', dd$Variable)][1]`  
Q13 = `r dd$allowed_values[grep('Q13', dd$Variable)][1]`

People who rate money as being more important are more likely to be required to go to work.  **Does not replicate**  

Q14 = `r dd$Question[grep('Q14', dd$Variable)][1]`  
Q14 = `r dd$allowed_values[grep('Q14', dd$Variable)][1]`  

**Replationship not found in primary sample.**

Q24 = `r dd$Question[grep('Q24', dd$Variable)][1]`  
Q24 = `r dd$allowed_values[grep('Q24', dd$Variable)][1]`  

**Replationship not found in primary sample.**

Q25 = `r dd$Question[grep('Q25', dd$Variable)][1]`  
Q25 = `r dd$allowed_values[grep('Q25', dd$Variable)][1]`  

**Replationship not found in primary sample.**

SC0 = `r dd$Question[grep('SC0', dd$Variable)][1]`  

**Replationship not found in primary sample.**

SC1 = `r dd$Question[grep('SC1', dd$Variable)][1]`

**People who rate money as being more important are more likely to experience more mental health symptoms.**

```{r money2, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table2[c(2:7), c(1,16)] %>%
    kable() %>%
    kable_styling() 
} else {
  table2[c(2:7), c(1,16)] %>%
    kable() %>%
    kable_styling() %>% 
    row_spec(c(3,4), bold = T, background = "yellow")
}
```

Q16_3 = `r dd$Question[grep('Q16_3', dd$Variable)][1]`  
Q16_3 = `r dd$allowed_values[grep('Q16_3', dd$Variable)][1]` 

**Relationship not found in primary sample.**

Q16_4 = `r dd$Question[grep('Q16_4', dd$Variable)][1]`  
Q16_4 = `r dd$allowed_values[grep('Q16_4', dd$Variable)][1]` 

**Relationship not found in primary sample.**

```{r money3, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table3[c(2:7), c(1,16)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(2,6), bold = T, background = "yellow")
} else {
  table3[c(2:7), c(1,16)] %>%
    kable() %>%
    kable_styling()
}
```

(lower scores = higher rank)  
Q20_2 = `r dd$Question[grep('Q20_2', dd$Variable)]`  

People who rate money as being more important are less likely to highly rank having people visit to deliver essential items.  **Did not replicate.**

Q20_6 = `r dd$Question[grep('Q20_6', dd$Variable)]`  

People who rate money as being more important are more likely to highly rank having people visit for essential care.  **Did not replicate.**

```{r money4, echo = FALSE, warnings = FALSE}
table4[c(2:6), c(1,8)] %>%
  kable() %>%
  kable_styling() 
```

## Importance of Social (Q169_2)
Q169_2 = `r dd$Question[grep('Q169_2', dd$Variable)][1]`  

```{r social, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table1[c(2:10,14:16), c(1,13)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(4), bold = T, background = "yellow") 
} else {
  table1[c(2:10,14:16), c(1,13)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(8,10), bold = T, background = "yellow")   
}
```

Q13 = `r dd$Question[grep('Q13', dd$Variable)][1]`  
Q13 = `r dd$allowed_values[grep('Q13', dd$Variable)][1]`

People who rate social contact as being more important are more likely to be required to go to work.  **Does not replicate.**

Q24_1 = `r dd$Question[grep('Q24_1', dd$Variable)][1]`  
Q24_1 = `r dd$allowed_values[grep('Q24_1', dd$Variable)][1]`

**Relationship not found in primary sample.**

SC0 = `r dd$Question[grep('SC0', dd$Variable)][1]`  
SC0 = `r dd$allowed_values[grep('SC0', dd$Variable)][1]`

**Relationship not found in primary sample.**

```{r social2, echo = FALSE, warnings = FALSE}
table2[c(2:7), c(1,10)] %>%
  kable() %>%
  kable_styling() 
```

```{r social3, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table3[c(2:7), c(1,10)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(1:3,6), bold = T, background = "yellow") 
} else {
  table3[c(2:7), c(1,10)] %>%
    kable() %>%
    kable_styling()
}
```

Q20_1 = `r dd$Question[grep('Q20_1', dd$Variable)]`  

People who rate social contact as being more importantare less likely to highly rank having people visit for work.  **Does not replicate.**

Q20_2 = `r dd$Question[grep('Q20_2', dd$Variable)]` 

People who rate social contact as being more importantare less likely to highly ranke having people visit to deliver essential items.  **Does not replicate.**

Q20_3 = `r dd$Question[grep('Q20_3', dd$Variable)]`  

People who rate social contact as being more important are more likely to highly rank having people visit for social contact.  **Does not replicate.**

Q20_6 = `r dd$Question[grep('Q20_6', dd$Variable)]`  

People who rate social contact as being more important are more likely to highly rank having people visit for essential care.  **Does not replicate.**

```{r social4, echo = FALSE, warnings = FALSE}
table4[c(2:6), c(1,9)] %>%
  kable() %>%
  kable_styling() 
```

## Importance of Health (Q169_3)
Q169_3 = `r dd$Question[grep('Q169_3', dd$Variable)][1]`  

```{r health, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table1[c(2:10,14:16), c(1,14)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(1,8), bold = T, background = "yellow")
} else {
  table1[c(2:10,14:16), c(1,14)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(7,8, 10), bold = T, background = "yellow")
}
```

Q10 = `r dd$Question[grep('Q10', dd$Variable)][1]`  
Q10 = `r dd$allowed_values[grep('Q10', dd$Variable)][1]`

People who rate health improvement as being more important are more likely to have COVID-19 (or sympotoms).  **Does not replicate.**

Q23_1 = `r dd$Question[grep('Q23_1', dd$Variable)][1]`  
Q23_1 = `r dd$allowed_values[grep('Q23_1', dd$Variable)][1]`

**Relationship not found in primary sample.**  

Q24_1 = `r dd$Question[grep('Q24_1', dd$Variable)][1]`  
Q24_1 = `r dd$allowed_values[grep('Q24_1', dd$Variable)][1]`

**People who rate health improvement as being more important are more worried about catching COVID-19. This replicates.**

SC0 = `r dd$Question[grep('SC0', dd$Variable)][1]`  
SC0 = `r dd$allowed_values[grep('SC0', dd$Variable)][1]`

**Relationship not found in primary sample.**  

```{r health2, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table2[c(2:7), c(1,11)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(3), bold = T, background = "yellow")
} else {
  table2[c(2:7), c(1,11)] %>%
    kable() %>%
    kable_styling()
}
```

Q16_3 = `r dd$Question[grep('Q16_3', dd$Variable)][1]` 

People who rate health improvement as being more important are less likely to highly rank leaving for social contact.  **Does not replicate.**

```{r health3, echo = FALSE, warnings = FALSE}
table3[c(2:7), c(1,11)] %>%
  kable() %>%
  kable_styling()
```

```{r health4, echo = FALSE, warnings = FALSE}
table4[c(2:6), c(1,10)] %>%
  kable() %>%
  kable_styling() 
```

## Value Difference (Social - Health; valuediff) 
```{r diff, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table1[c(2:10,14:16), c(1,22)] %>%
    kable() %>%
    kable_styling() 
} else {
  table1[c(2:10,14:16), c(1,22)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(11), bold = T, background = "yellow")
}
```

SC1 = `r dd$Question[grep('SC1', dd$Variable)][1]` 

**Relationship not present in primary sample.**

```{r diff2, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table2[c(2:7), c(1,16)] %>%
    kable() %>%
    kable_styling()
} else {
  table2[c(2:7), c(1,16)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(3), bold = T, background = "yellow")
}
```

Q16_3 = `r dd$Question[grep('Q16_3', dd$Variable)][1]` 

**Relationship not present in primary sample.**

```{r diff3, echo = FALSE, warnings = FALSE}
if (sample == 1) {
  table3[c(2:7), c(1,16)] %>%
    kable() %>%
    kable_styling() %>%
    row_spec(c(2,6), bold = T, background = "yellow")
} else {
  table3[c(2:7), c(1,16)] %>%
    kable() %>%
    kable_styling()
  }
```

Q20_2 = `r dd$Question[grep('Q20_2', dd$Variable)]` 

People who rate social contact as being more important than health are less likely to highly rank having people visit to deliver essential items. **Does not replicate.**

Q20_6 = `r dd$Question[grep('Q20_6', dd$Variable)]`  

People who rate social contact as being more important than health are more likely to highly rank having people visit for essential care. **Does not replicate.**

```{r diff4, echo = FALSE, warnings = FALSE}
table4[c(2:6), c(1,15)] %>%
  kable() %>%
  kable_styling() 
```