---
title: "Values and Social Distancing"
author: "Kendra Seaman"
date: "5/29/2020"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
```

```{r scripts, include = FALSE}
source("../08_social_dist_correlations.R")
```

## Importance of Money (Q169_1)
Q169_1 = `r dd$Question[grep('Q169_1', dd$Variable)][1]`  

```{r money, echo = FALSE, warnings = FALSE}
table1[c(2:10,14:16), c(1,12)] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(4, 11), bold = T, background = "yellow")
```

Q13 = `r dd$Question[grep('Q13', dd$Variable)][1]`  
Q13 = `r dd$allowed_values[grep('Q13', dd$Variable)][1]`

**People who rate money as being more important are more likely to be required to go to work.**

SC1 = `r dd$Question[grep('SC1', dd$Variable)][1]`

**People who rate money as being more important are more likely to experience more mental health symptoms.**

```{r money2, echo = FALSE, warnings = FALSE}
table2[c(2:7), c(1,16)] %>%
  kable() %>%
  kable_styling() 
```

```{r money3, echo = FALSE, warnings = FALSE}
table3[c(2:7), c(1,16)] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(2,6), bold = T, background = "yellow")
```

(lower scores = higher rank)  
Q20_2 = `r dd$Question[grep('Q20_2', dd$Variable)]`  

**People who rate money as being more important are less likely to highly rank having people visit to deliver essential items.**

Q20_6 = `r dd$Question[grep('Q20_6', dd$Variable)]`  

**People who rate money as being more important are more likely to highly rank having people visit for essential care.**

```{r money4, echo = FALSE, warnings = FALSE}
table4[c(2:6), c(1,8)] %>%
  kable() %>%
  kable_styling() 
```

## Importance of Social (Q169_2)
Q169_2 = `r dd$Question[grep('Q169_2', dd$Variable)][1]`  

```{r social, echo = FALSE, warnings = FALSE}
table1[c(2:10,14:16), c(1,13)] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(4), bold = T, background = "yellow")
```

Q13 = `r dd$Question[grep('Q13', dd$Variable)][1]`  
Q13 = `r dd$allowed_values[grep('Q13', dd$Variable)][1]`

**People who rate social contact as being more important are more likely to be required to go to work.**

```{r social2, echo = FALSE, warnings = FALSE}
table2[c(2:7), c(1,10)] %>%
  kable() %>%
  kable_styling() 
```

```{r social3, echo = FALSE, warnings = FALSE}
table3[c(2:7), c(1,10)] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(1:3,6), bold = T, background = "yellow")
```

Q20_1 = `r dd$Question[grep('Q20_1', dd$Variable)]`  

**People who rate social contact as being more importantare less likely to highly rank having people visit for work.**

Q20_2 = `r dd$Question[grep('Q20_2', dd$Variable)]` 

**People who rate social contact as being more importantare less likely to highly ranke having people visit to deliver essential items.**

Q20_3 = `r dd$Question[grep('Q20_3', dd$Variable)]`  

**People who rate social contact as being more important are more likely to highly rank having people visit for social contact.**

Q20_6 = `r dd$Question[grep('Q20_6', dd$Variable)]`  

**People who rate social contact as being more important are more likely to highly rank having people visit for essential care.**

```{r social4, echo = FALSE, warnings = FALSE}
table4[c(2:6), c(1,9)] %>%
  kable() %>%
  kable_styling() 
```

## Importance of Health (Q169_3)
Q169_3 = `r dd$Question[grep('Q169_3', dd$Variable)][1]`  

```{r health, echo = FALSE, warnings = FALSE}
table1[c(2:10,14:16), c(1,14)] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(1,8), bold = T, background = "yellow")
```

Q10 = `r dd$Question[grep('Q10', dd$Variable)][1]`  
Q10 = `r dd$allowed_values[grep('Q10', dd$Variable)][1]`

**People who rate health improvement as being more important are more likely to have COVID-19 (or sympotoms).**

Q24_1 = `r dd$Question[grep('Q24_1', dd$Variable)][1]`  
Q24_1 = `r dd$allowed_values[grep('Q24_1', dd$Variable)][1]`

**People who rate health improvement as being more important are more worried about catching COVID-19.**

```{r health2, echo = FALSE, warnings = FALSE}
table2[c(2:7), c(1,11)] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(3), bold = T, background = "yellow")
```

Q16_3 = `r dd$Question[grep('Q16_3', dd$Variable)][1]` 

**People who rate health improvement as being more important are less likely to highly rank leaving for social contact.**

```{r health3, echo = FALSE, warnings = FALSE}
table3[c(2:7), c(1,11)] %>%
  kable() %>%
  kable_styling()
```

```{r health4, echo = FALSE, warnings = FALSE}
table4[c(2:6), c(1,10)] %>%
  kable() %>%
  kable_styling() 
```

## Value Difference (Social - Health; valuediff) 
```{r diff, echo = FALSE, warnings = FALSE}
table1[c(2:10,14:16), c(1,22)] %>%
  kable() %>%
  kable_styling() 
```

```{r diff2, echo = FALSE, warnings = FALSE}
table2[c(2:7), c(1,16)] %>%
  kable() %>%
  kable_styling()
```

```{r diff3, echo = FALSE, warnings = FALSE}
table3[c(2:7), c(1,16)] %>%
  kable() %>%
  kable_styling() %>%
  row_spec(c(2,6), bold = T, background = "yellow")
```

Q20_2 = `r dd$Question[grep('Q20_2', dd$Variable)]` 

**People who rate social contact as being more important than health are less likely to highly rank having people visit to deliver essential items.**

Q20_6 = `r dd$Question[grep('Q20_6', dd$Variable)]`  

**People who rate social contact as being more important than health are more likely to highly rank having people visit for essential care.**

```{r diff4, echo = FALSE, warnings = FALSE}
table4[c(2:6), c(1,15)] %>%
  kable() %>%
  kable_styling() 
```